% experience.tex
\section*{Professional Experience}

{\companyfont Airbus Defence and Space} \hfill \textcolor{shadeGray}{March 2026 – present}

{\rolefont Working Student — AI Tool Development} \hfill 
\textit{\textcolor{shadeGray}{Software Engineering · Agentic AI · LLMs}}


\subsectionspacing


{\companyfont Hitachi Rail GTS Deutschland} \hfill \textcolor{shadeGray}{February 2025 – February 2026}

{\rolefont Working Student — Penetration Testing} \hfill 
\textit{\textcolor{shadeGray}{Cybersecurity · Kali Linux · Penetration Testing · Jenkins}}

\begin{itemize}
\item Performed penetration testing on railway systems and products.
\item Created and maintained custom Kali Linux ISO with automated builds using Jenkins.
\item Developed a custom Burp Suite plugin to simulate railway-specific traffic protocols for security testing purposes.

\end{itemize}


\subsectionspacing


{\companyfont DENSO Automotive Deutschland} \hfill \textcolor{shadeGray}{October 2023 – November 2024}

{\rolefont Working Student — Fundamental Technology R\&D} \hfill
\textit{\textcolor{shadeGray}{Apache Kafka · Cybersecurity · Python}}

\vspace{0.3em}
CONNECT Horizon Europe research program focusing on Trust Management in VANETs.
\begin{itemize}    
    \item Implemented, tested, and maintained a Python-based Cooperative Adaptive Cruise Control (CACC) module within SUMO traffic simulations, using Apache Kafka for real-time vehicle communication on Ubuntu Linux.
    \item Integrated communication between the Trust Assessment Framework (TAF) and partner systems to dynamically migrate CACC instances between ECUs based on Trust Levels.
\end{itemize}


\subsectionspacing


{\companyfont Mercedes-Benz Tech Innovation} \hfill \textcolor{shadeGray}{October 2021 – September 2023}

{\rolefont Working Student — CarIT Security} \hfill
\textit{\textcolor{shadeGray}{Cybersecurity · Project Management · Python}}

\begin{itemize}
    \item Developed a Python-based tool for automated cybersecurity analysis of vehicular network architectures.
    \item Performed vulnerability analysis on vehicle systems to identify security weaknesses.
    \item Assisted with project management tasks, including documentation and review processes.
\end{itemize}
\textit{Bachelor's  Thesis}
\begin{itemize}
    \item "Comparing different vehicle architectures based on attack path analysis".
\end{itemize}

\subsectionspacing
\subsectionspacing